\emph{hp}-Finite Element Model of Poisson and Nernst-Planck System of Equations

### 2010-09-28 results.tex
some modifications in figure order in results

\begin{figure}
  \begin{centering}
  \includegraphics[width=.75\columnwidth]{cphi}
  \caption{\label{fig:cphi} Concentration $C$
  and voltage $\phi$ at two different time steps
  (HP\_ANISO adaptivity was used).}
  \end{centering}
\end{figure}

We ran the calculation for all the adaptivity types 
in both single-mesh and multi-mesh configurations. 
Example of the solution at $t=0.7\ s$ and $t=3.0\ s$ 
with adaptivity type HP\_ANISO is shown
in Fig.~\ref{fig:cphi}. The time $t=0.7\ s$ was chosen because
by that time, some ionic migration has already taken place, i.e.
concentration gradient near the $\partial\Omega_1$ and
$\partial\Omega_3$ has formed. The automatic mesh refinements
at different time steps are clearly visible --- especially
near the top boundary, where the concentration gradient is
moving in time (as seen in Fig.~\ref{fig:comsol-conc-volt}).

The following numeric results were recorded for each 
adaptivity type: converged error at each time step, cumulative CPU
time at each time step, and the problem size in terms of number
of degrees of freedoms (NDOFs) at each time step.  
Two types of initial meshes were used --- in case of only \emph{p}-adaptivity,
more refined mesh was used. When also the element size refinement
was enabled (all \emph{h} adaptivity types), very coarse initial mesh
was used. In any case, the initial mesh was loaded at each time step.

\begin{figure}
  \begin{centering}
  \includegraphics[width=.8\columnwidth]{mesh}
  \caption{\label{fig:mesh} Initial coarse mesh (a),
  	half refined mesh (b) and refined mesh (c). The coarse mesh
	and refined mesh were used in the initial calcualtions, the latter one
	in case of \emph{p}-adaptivity (including HP\_ANISO\_P). The half-refined mesh was
	used later to optimize \emph{hp}-adaptive mode solutions.}
  \end{centering}
\end{figure}

@@

Fig.~\ref{fig:cpu} shows the cumulative CPU time for different adaptivity
modes at each time step. All the calculations were done on the same computer.
Here we see that HP\_ANISO requires the most
resources which can be understood from the fact that this adaptivity mode has the largest number of 
candidates (see XXX) from which the refinement methode is chosen.
At the same time, HP\_ANISO\_H is the fastest.
Fig.~\ref{fig:dof} shows the NDOFs at each time step for different adaptivity modes.
There we see that the HP\_ANISO results in the smallest problem size --- $N_{dof} \approx 125$. 
All the other adaptivity modes result in  the problem size approximately ($N_{dof} \approx 300$), 
however, \emph{p}-adaptivity modes P\_ISO and P\_ANISO start off with relatively large $N_{dof}$.
We can see from the graphs and also from the Fig.~\ref{fig:mesh} that
\emph{p}-adaptivity is used for the most part of the problem. The initially high
$N_{dof}$ for \emph{p}-adaptive modes indicate that only first time steps benefit
greatly from the \emph{h}-adaptivity. P\_ISO, HP\_ANISO\_H
and HP\_ANISO\_P are the fastest in terms of CPU time, however, we have to consider
that P\_ISO  and HP\_ANISO\_P start off from more refined mesh.

>>>>

\begin{figure}
  \begin{centering}
  \includegraphics[width=.8\columnwidth]{mesh}
  \caption{\label{fig:mesh} Initial coarse mesh (a),
  	half refined mesh (b) and refined mesh (c). The coarse mesh
	and refined mesh were used in the initial calcualtions, the latter one
	in case of \emph{p}-adaptivity (including HP\_ANISO\_P). The half-refined mesh was
	used later to optimize \emph{hp}-adaptive mode solutions.}
  \end{centering}
\end{figure}
We ran the calculation for all the adaptivity types 
in both single-mesh and multi-mesh configurations. 
The following numeric results were recorded for each 
adaptivity type: converged error at each time step, cumulative CPU
time at each time step, and the problem size in terms of number
of degrees of freedoms (NDOFs) at each time step.  
Two types of initial meshes were used --- in case of only \emph{p}-adaptivity,
more refined mesh was used. When also the element size refinement
was enabled (all \emph{h} adaptivity types), very coarse initial mesh
was used. In any case, the initial mesh was loaded at each time step.

\begin{figure}
  \begin{centering}
  \includegraphics[width=.75\columnwidth]{cphi}
  \caption{\label{fig:cphi} Concentration $C$
  and voltage $\phi$ at two different time steps
  (HP\_ANISO adaptivity was used).}
  \end{centering}
\end{figure}
Example of the solution at $t=0.7\ s$ and $t=3.0\ s$ 
with adaptivity type HP\_ANISO is shown
in Fig.~\ref{fig:cphi}. The time $t=0.7\ s$ was chosen because
by that time, some ionic migration has already taken place, i.e.
concentration gradient near the $\partial\Omega_1$ and
$\partial\Omega_3$ has formed. The automatic mesh refinements
at different time steps are clearly visible --- especially
near the top boundary, where the concentration gradient is
moving in time (as seen in Fig.~\ref{fig:comsol-conc-volt}).

@@

Fig.~\ref{fig:cpu} shows the cumulative CPU time for different adaptivity
modes at each time step. All the calculations were done on the same computer.
Here we see that HP\_ANISO requires the most
resources which can be understood from the fact that this adaptivity mode has the largest number of 
candidates (see XXX) from which the refinement methode is chosen.
At the same time, HP\_ANISO\_H is the fastest.
Fig.~\ref{fig:dof} shows the NDOFs at each time step for different adaptivity modes.
There we see that the HP\_ANISO results in the smallest problem size --- $N_{dof} \approx 125$. 
All the other adaptivity modes result in  the problem size approximately ($N_{dof} \approx 300$), 
however, \emph{p}-adaptivity modes P\_ISO and P\_ANISO start off with relatively large $N_{dof}$.
We can see from the graphs and also from the Fig.~\ref{fig:cphi} that
\emph{p}-adaptivity is used for the most part of the problem. The initially high
$N_{dof}$ for \emph{p}-adaptive modes indicate that only first time steps benefit
greatly from the \emph{h}-adaptivity. P\_ISO, HP\_ANISO\_H
and HP\_ANISO\_P are the fastest in terms of CPU time, however, we have to consider
that P\_ISO  and HP\_ANISO\_P start off from more refined mesh.
